### 2020-04-23 reports/thesis/chapters/5_inference.tex
Final corrections

It is interesting to compare the empirical null standard deviation with MADA-mode, in Figure \ref{fig:inference_NullIidStd}, because they both depend on the mode. The mode suffered from high variance which may affect dispersion estimators using the mode. The figure shows that MADA-mode has less variance than the empirical null standard deviation. This suggests that using the curvature of the density estimate at the mode is the main source of variance for the empirical null standard deviation.

>>>>

It is interesting to compare the empirical null standard deviation with MADA-mode, in Figure \ref{fig:inference_NullIidStd}, because they both depend on the mode. The mode suffered from high variance which may affect dispersion estimators using the mode. The figure shows that MADA-mode had less variance than the empirical null standard deviation. This suggests that using the curvature of the density estimate at the mode was the main source of variance for the empirical null standard deviation.
